Efficient pedigree recording for fast population genetics simulation

### 2017-12-27 forwards_paper.tex
minor rewording

Figure~\ref{fig:wf-trees} shows
an example of a marginal genealogy produced by a forwards-time Wright--Fisher
process like Algorithm~\algref{W}.
On the left is the tree showing all the edges output by the simulation,
while on the right
is the minimal tree representing the ancestry of the currently alive population.
Clearly there is a great deal of redundancy in the topological
information output by the simulation.
This redundancy comes from two sources.
First, there are a large number of nodes in tree that have only one child.
In Algorithm~\algref{W} we do not attempt to identify coalescence events,
but simply record all parent-child
relationships in the history of the population.
As such, many of these edges
will record the simple passing of genealogical information from parent to child
and only some small subset will correspond to coalescences within the marginal
trees. The second source of redundancy in the output of Algorithm~\algref{W}
is due to the fact that lineages die out: a large number of
individuals in the simulation leave no descendants in the present day population.
Node 26 in Figure~\ref{fig:wf-trees}a, for example, leaves no
ancestors in the current population, and so the entire path tracing back to
the root is redundant.

>>>>

Figure~\ref{fig:wf-trees} shows
an example of a marginal genealogy produced by a forwards-time Wright--Fisher
process like Algorithm~\algref{W}.
On the left is the tree showing all the edges output by the simulation,
while on the right
is the minimal tree representing the ancestry of the current generation of the population.
Clearly there is a great deal of redundancy in the topological
information output by the simulation.
This redundancy comes from two sources.
First, there are a large number of nodes in tree that have only one child.
In Algorithm~\algref{W} we do not attempt to identify coalescence events,
but simply record all parent-child
relationships in the history of the population.
As such, many of these edges
will record the simple passing of genealogical information from parent to child
and only some small subset will correspond to coalescences within the marginal
trees. The second source of redundancy in the output of Algorithm~\algref{W}
is due to the fact that lineages die out: a large number of
individuals in the simulation leave no descendants in the present day population.
Node 26 in Figure~\ref{fig:wf-trees}a, for example, leaves no
ancestors in the current population, and so the entire path tracing back to
the root is redundant.
